The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-23 paper/ms.tex
Almost all figures with big labels and in .eps
restoring section on the radiative transfer codes

Additionally, we have used two independently developed Monte Carlo
codes \cite{CLARA,DijkstraKramer} to perform the calculations of the
non-dusty models. The results we report are robust in the sense
that they are obtained by both codes.

@@

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
\end{center}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{maximumVvsVmax.png}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{NscattvsVmax.png}
\caption{Logarithm of the average number of scatterings as function of
  rotational velocity velocity. Continuous (dashed) lines represent an
  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
  \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}\\
  \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
  \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}    
\end{center}
    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
      show the homogeneous (central) source distribution. Left
      corresponds to the static case and the right
      $V_{max}=300km/s$. The color scale is logarithmic on the
      number of photons with given values of $N_{\rm scatt}$ and
      $x$. \label{fig:Nscatt2D}}   
\end{figure*}

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{escapefraction.png}
   \caption{Escape fraction as a function of rotational velocity, for these models we took $\tau_{a}=1$. The
     continuous (dashed) lines correspond to central (homogeneous)
     models.
     \label{fig:efvsv}}
\end{figure}

\begin{figure}
  \includegraphics[width=0.45\textwidth]{Neufeld.png}
 \caption{Escape fraction as a function of the
   product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
   the infinite slab is shown as a continuous line. Different dashed
   lines correspond to different rotational velocities, for this models 
   $\tau_a = 1$.
   \label{fig:efvsNeufeld}}   
\end{figure}

@@

\subsection{Off-Centered emission}
\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.3]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centered emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (where the reader is) 
    and the observer is along the $\hat{\j}$ direction. 
    \label{fig:OCspheres}} 
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.35]{muhisto.png}
  \caption{$\mu$ histogram showing the orientation effects for the different
  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
    \label{fig:muhisto}} 
\end{figure}

@@

\begin{figure*}
\includegraphics[scale=0.3]{OC_profiles.png}
\caption{\ly profiles for the off-center positions for all of our models, Dashed/solid
  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
   \label{fig:OC_profiles}} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[scale=0.3]{3peaks.png}
\caption{Three-Peak profiles for three different off-center positions $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid line) and for different rotational velocities. 
   \label{fig:3p_profiles}} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[scale=0.3]{3p_res.png}
\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
   \label{fig:3p_res}} 
\end{figure*}

>>>>

@@

Additionally, we have used two independently developed Monte Carlo
codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
non-dusty models. The results we report are robust in the sense
that they are obtained by both codes.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{f1_1.eps}
  \includegraphics[width=0.45\textwidth]{f1_2.eps}
\end{center}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{f3.eps}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{f4.eps}
\caption{Logarithm of the average number of scatterings as function of
  rotational velocity velocity. Continuous (dashed) lines represent an
  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{f5_1.eps}
  \includegraphics[width=0.45\textwidth]{f5_2.eps}\\
  \includegraphics[width=0.45\textwidth]{f5_3.eps}
  \includegraphics[width=0.45\textwidth]{f5_4.eps}    
\end{center}
    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
      show the homogeneous (central) source distribution. Left
      corresponds to the static case and the right
      $V_{max}=300km/s$. The color scale is logarithmic on the
      number of photons with given values of $N_{\rm scatt}$ and
      $x$. \label{fig:Nscatt2D}}   
\end{figure*}

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{f6.eps}
   \caption{Escape fraction as a function of rotational velocity, for these models we took $\tau_{a}=1$. The
     continuous (dashed) lines correspond to central (homogeneous)
     models.
     \label{fig:efvsv}}
\end{figure}

\begin{figure}
  \includegraphics[width=0.45\textwidth]{f7.eps}
 \caption{Escape fraction as a function of the
   product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
   the infinite slab is shown as a continuous line. Different dashed
   lines correspond to different rotational velocities, for this models 
   $\tau_a = 1$.
   \label{fig:efvsNeufeld}}   
\end{figure}

@@

\subsection{Off-Centered emission}
\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.3]{f8.eps}
  \caption{The two solid circles show the two different spherical
    off-centered emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (where the reader is) 
    and the observer is along the $\hat{\j}$ direction. 
    \label{fig:OCspheres}} 
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.35]{f9.eps}
  \caption{$\mu$ histogram showing the orientation effects for the different
  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
    \label{fig:muhisto}} 
\end{figure}

@@

\begin{figure*}
\includegraphics[scale=0.3]{f10.eps}
\caption{\ly profiles for the off-center positions for all of our models, Dashed/solid
  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
   \label{fig:OC_profiles}} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[scale=0.3]{f11.eps}
\caption{Three-Peak profiles for three different off-center positions $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid line) and for different rotational velocities. 
   \label{fig:3p_profiles}} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[scale=0.3]{f12.eps}
\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
   \label{fig:3p_res}} 
\end{figure*}
